### 2019-08-01 reports/thesis/chapters/3_compoundPoisson.tex
Made CpEmAlgorithm an Experiment

\begin{figure}[p]
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_lnL.eps}
        \caption{Log likelihood}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_lambda.eps}
        \caption{$\lambda$}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_alpha.eps}
        \caption{$\alpha$}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_beta.eps}
        \caption{$\beta$}
    \end{subfigure}
    }
    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times. The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment. The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
    \label{fig:compoundPoisson_convergence_1}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_lnL.eps}
        \caption{Log likelihood}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_lambda.eps}
        \caption{$\lambda$}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_alpha.eps}
        \caption{$\alpha$}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_beta.eps}
        \caption{$\beta$}
    \end{subfigure}
    }
    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times. The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment. The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
    \label{fig:compoundPoisson_convergence_2}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_lnL.eps}
        \caption{Log likelihood}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_lambda.eps}
        \caption{$\lambda$}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_alpha.eps}
        \caption{$\alpha$}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_beta.eps}
        \caption{$\beta$}
    \end{subfigure}
    }
    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(10,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times. The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment. The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
    \label{fig:compoundPoisson_convergence_3}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_lnL.eps}
        \caption{Log likelihood}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_lambda.eps}
        \caption{$\lambda$}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_alpha.eps}
        \caption{$\alpha$}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_beta.eps}
        \caption{$\beta$}
    \end{subfigure}
    }
    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(100,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times. The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment. The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
    \label{fig:compoundPoisson_convergence_4}
\end{figure}

>>>>

\begin{figure}[p]
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_lnL.eps}
        \caption{Log likelihood}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_lambda.eps}
        \caption{$\lambda$}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_alpha.eps}
        \caption{$\alpha$}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_beta.eps}
        \caption{$\beta$}
    \end{subfigure}
    }
    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times. The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment. The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
    \label{fig:compoundPoisson_convergence_1}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_lnL.eps}
        \caption{Log likelihood}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_lambda.eps}
        \caption{$\lambda$}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_alpha.eps}
        \caption{$\alpha$}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_beta.eps}
        \caption{$\beta$}
    \end{subfigure}
    }
    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times. The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment. The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
    \label{fig:compoundPoisson_convergence_2}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_lnL.eps}
        \caption{Log likelihood}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_lambda.eps}
        \caption{$\lambda$}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_alpha.eps}
        \caption{$\alpha$}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_beta.eps}
        \caption{$\beta$}
    \end{subfigure}
    }
    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(10,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times. The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment. The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
    \label{fig:compoundPoisson_convergence_3}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_lnL.eps}
        \caption{Log likelihood}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_lambda.eps}
        \caption{$\lambda$}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_alpha.eps}
        \caption{$\alpha$}
    \end{subfigure}
        \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_beta.eps}
        \caption{$\beta$}
    \end{subfigure}
    }
    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(100,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times. The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment. The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
    \label{fig:compoundPoisson_convergence_4}
\end{figure}

\afterpage{\clearpage}
